---
title: "connectapi Tags"
author: "Cole Arendt"
date: "7/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(connectapi)
client <- connect(prefix = "TEST_1")
options("connectapi_disable_experimental_warnings" = TRUE)
```

# Getting Started

To understand how tags work with `connectapi`, you must first understand tags in
RStudio Connect.

- Tags in RStudio Connect consist of multiple "tag trees," each with a "Category"
as its parent.
- The tag hierarchy / structure is created by administrators
- Publishers and administrators can associate any non-Category tag with content
- A tag being a member of a "child" tag doe _not_ automatically make it a member
of the "parent" tag

As always, get started by defining the `CONNECT_SERVER` and `CONNECT_API_KEY`
variables, then initialize an API client.

```{r eval=FALSE}
library(connectapi)
client <- connect()
```

**NOTE:** This example report will create a few tag hierarchies and then use
them. As a result, to use this example verbatim requires admin privileges and
_will_ create tags on your server.

# Create the Tag Tree(s)

To get started, we will create a tag tree to show how things work. The
`create_tag()` helper allows you to create a singular tag (by specifying its
parent, etc.). For our purposes, `create_tag_tree()` is easier, since it
creates the entire tree specified at once.

```{r get_tags}
start_tags <- get_tags(client)
start_tags
```

```{r check_tag_exist, include=FALSE}
# Protect against tags already existing
if ("DemoProject" %in% names(start_tags) || "DemoAudience" %in% names(start_tags)) {
  stop("ERROR: One of the demo tags already exist for you! Beware lest they be deleted by this demo")
}
```

```{r create_demo_tags}
tree_project_1 <- create_tag_tree(client, "DemoProject", "project_1")
tree_project_1

tmp_tags <- get_tags(client)

tree_project_2 <- create_tag(client, name = "project_2", parent = tmp_tags$DemoProject)
tree_project_2

tree_audience_1 <- create_tag_tree(client, "DemoAudience", "Sales")
tree_audience_2 <- create_tag_tree(client, "DemoAudience", "Finance")

get_tags(client)
```

# Content tags

In order to show how tags work, we need some content to work with.

```{r content_deploy}
bnd <- bundle_static(system.file("logo.png", package = "connectapi"))

content_1 <- deploy(client, bnd)
content_2 <- deploy(client, bnd)
```

## Set Tags

Content 1 is for `project_1` and `Sales`, so let's set the tags!
There are a few ways to do so.

```{r content_1_tags}
all_tags <- get_tags(client)

set_content_tag_tree(content_1, "DemoProject", "project_1")

set_content_tags(content_1, all_tags$DemoAudience$Sales)
```
Content 2 is for `project_2` and both Audiences (`Sales` and `Finance`).

```{r content_2_tags}
set_content_tags(
  content_2,
  all_tags$DemoProject$project_2,
  all_tags$DemoAudience$Sales,
  all_tags$DemoAudience$Finance
)
```

## See the tags associated with content

In order to see the tags associated with content, use `get_content_tags()`.
The data structure is the same as `get_tags()`, but the "whole list" is filtered
to only the tags that are associated with a piece of content.

```{r}
c1_tags <- get_content_tags(content_1)
c1_tags

c2_tags <- get_content_tags(content_2)
c2_tags
```

# List all content associated with a tag

Once tags have been defined, you can also search for all of the content
associated with a tag. 

```{r}
content_list_by_tag(client, all_tags$DemoAudience$Sales)

content_list_by_tag(client, all_tags$DemoProject$project_1)

content_list_by_tag(client, all_tags$DemoProject)
```

# Cleanup

Now we will clean up the demo tags that we created.

```{r cleanup}
# Protect against tags already existing
if ("DemoProject" %in% names(start_tags) || "DemoAudience" %in% names(start_tags)) {
  stop("ERROR: One of the demo tags already exist for you! Beware lest they be deleted by this demo")
}

latest_tags <- get_tags(client)
delete_tag(client, latest_tags$DemoProject)
delete_tag(client, latest_tags$DemoAudience)

# TODO: delete content
```


